A Decision Procedure for String Constraints with {\parseInt} Function and Flat Regular Constraints

### 2021-05-06 FMCAD2021/paper.tex
rename

\documentclass[runningheads]{llncs}

@@

\RequirePackage{todonotes}
%\newcommand{\znj}[1]{\todo[inline,color=orange!10]{\textbf{ZHAN:} #1}}
\newcommand{\znjSide}[1]{\todo[color=orange!10]{\textbf{ZHAN:} #1}}
\newcommand\znj[1]{\textcolor{red}{#1}}

\newcommand{\parseInt}{\textsf{parseInt}}
\newcommand{\paexp}{$\textsf{PA}_{\exp}$}
%\newcommand{\paexp}{$(\mathbb{N},+,2^x)$}
\newcommand{\Def}{\hat{=}}

@@

\begin{abstract}
    The problem of solving string constraints is currently one of the focuses of theoretical computer science, particular related to SMT-based program verification, as it is inevitably that most of 
    programs manipulate string data structures. 
    The general problem of string constraint solving 
    is undecidable, therefore people try to identify 
    some sub-problems with decidability, e.g., string constraints restricted to generic flat languages. 
    Certainly, it is challenging and 
    makes theoretical and practical significance to 
    identify such subset with as much expressive power as possible. 
    In this paper, we identify 
    the subset of flat string constraints with 
     the string-number conversion function $\mathbf{parseInt}$, and 
     provide a decision procedure to the subset by reduction to
   the decidability problem of Presburger Arithmetic with exponential functions, 
    which is decidable. To the best of our knowledge, such a subset is 
    the largest subset of string constraints with decidability so far.

\keywords{ String Constraints \and Decidability \and Exponential Functions \and Quantifier Elimination.}

>>>>

% !TEX program = xelatex
\documentclass[runningheads]{llncs}

@@

\RequirePackage{todonotes}
\newcommand{\znjSide}[1]{\todo[color=orange!10]{\textbf{ZHAN:} #1}}
\newcommand\znj[1]{\textcolor{red}{#1}}
\newcommand{\parseInt}{\textsf{parseInt}}
\newcommand{\paexp}{$\textsf{PA}_{\exp}$}
\newcommand{\Def}{\hat{=}}

@@

\begin{abstract}
    String constraint solving is the core of various testing and verification approaches for scripting languages. 
    Among algorithms for solving string constraints, flattening is a well-known approach that is particularly useful in handling satisfiable instances.
    In the PLDI 2020 paper of Abdulla et al., the authors extended the flattening approach to support the string-integer conversion function, which appears in almost all scripting languages.
    However, their approach supports only a specific flattening pattern and leaves the support of the general class as an open problem.
    In this paper, we bridge the gap and propose a complete flattening approach for the string-integer conversion, based upon a decision procedure for solving the linear-exponential arithmetic constraints (namely, the extension of Presburger arithmetic with exponential functions).
    Besides the theoretical results, we also develop various optimizations and implement the decision procedure.
    Moreover, we evaluate the performance of the implementation on the benchmarks that are generated from the string hash functions as well as generated randomly.
    The experimental results show that our implementation outperforms the state-of-the-art solvers for string-integer constraints as well as linear-exponential constraints, in both precision and efficiency.
\keywords{ String Constraints \and Decidability \and Exponential Functions \and Quantifier Elimination.}
